Predicting Canadian Grocery Price Trends Using Bayesian Models

### 2024-12-02 paper/paper.qmd
Updated paper and datasheet

---
title: "Predicting Grocery Price Trends Using Bayesian Models"
subtitle: "An analysis of price patterns across Canadian grocery vendors to identify the most beneficial vendor for consumers"
author: Tina Kim
thanks: "Code and data are available at: https://github.com/thk421/Canadian-Grocery-Prices.git"
date: today
date-format: long
abstract: "This study uses Bayesian statistical models to analyze grocery price trends across eight Canadian vendors by examining current and historical grocery price data. Our findings show that vendor-specific factors and product type significantly influence price changes. This research provides actionable insights for consumers and vendors looking to optimize their grocery purchasing and pricing strategies while adhering to the 2019 Canada's Food Guide, especially in light of the growing demand for affordable, sustainable food choices."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

>>>>

---
title: "Predicting Canadian Grocery Price Trends Using Bayesian Models"
subtitle: "An analysis of price patterns across grocery vendors in Canada to identify the most beneficial vendor for consumers"
author: Tina Kim
thanks: "Code and data are available at: https://github.com/thk421/Canadian-Grocery-Prices.git"
date: today
date-format: long
abstract: "This study uses Bayesian statistical models to analyze grocery price trends across eight Canadian vendors by examining current and historical grocery price data. Our findings show that vendor-specific factors and product type significantly influence price changes. This research provides actionable insights for consumers and vendors looking to optimize their grocery purchasing and pricing strategies while adhering to the 2019 Canada's Food Guide, especially in light of the growing demand for affordable, sustainable food choices."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@fig-trace-plot shows the traceplots for the bayesian model. [Add more here]
